A Fully Decentralized Infrastructure for Automated and Trusted IoT Data Trading

### 2020-06-02 paper.tex
Add related work: data trading

\section{Related Work}
\label{section:relatedWork}
% pub/sub
\subsection{Data exchangement mechanism for IoT}
The publish/subscribe service model consists of publishers, subscribers and brokers, which has been proven\cite{pubSubAnalysis, pubSubAnalysis2} to be an efficient and flexible solution for a large number of diverse entities like IoT applications. A lot of work in publish/subscribe system focused on the scalability and the different security issues such as, encrypted data communication, privacy preserving data subscription and access control of digital asset. A few work targets on the storage which is a vital considerations for IoT and mobile computing and the incentive for data economics.

@@

\subsection{Decentralized Data Marketplace Infrastructure}
% decentralized DM

\subsection{Distributed Storage System}
% distributed data storage
Decentralized storage systems allow users to store files in a distributed network that is maintained by individual nodes around the world instead of a central service provider. Nevertheless, DLTs are often used as the backbone of these systems as data storage and also an incentive layer to encourage people get involved in the network. Filecoin \cite{FileCoin} in Inter-Planetary File system(IPFS)\cite{IPFS} is an incentive layer to incent nodes to provide storage. IPFS is a content-based addressing storage model in a peer-to-peer network, which users can obtain the data with the unique hash value through the network. However, no cryptographic system is applied for user-uploaded files. Sia\cite{Sia} splits the uploaded file into multiple data segments encrypted with the owner's private key, then cipher text is sent to the Sia nodes that rent the storage in Siacoin through smart contracts. Files are duplicated in multiple nodes to prevent data loss.

>>>>

\section{Related Work}
\label{section:relatedWork}
% pub/sub
\subsection{Data exchange mechanism for IoT}
The publish/subscribe service model consists of publishers, subscribers and brokers, which has been proven\cite{pubSubAnalysis, pubSubAnalysis2} to be an efficient and flexible solution for a large number of diverse entities like IoT applications. A lot of work in publish/subscribe system focused on the scalability and the different security issues such as, encrypted data communication, privacy preserving data subscription and access control of digital asset. A few work targets on the storage which is a vital considerations for IoT and mobile computing and the incentive for data economics.

@@

\subsection{Trusted IoT Trading Infrastructure}
Multiple infrastructures of trusted data marketplace for IoT data trading has been proposed. Paolo Missier et. al\cite{MindMyValue} presented an IoT brokered infrastructure based marketplace which enables the trading with Ethereum smart contracts. The brokers are only responsible for data transmission but matching publishers and subscribers as standard pub/sub model in order to adapt flexible agreement between participants. However, the data cubes (i.e., a tuple of information, such as provider, subscriber and time period) are stored in a centralized Cassandra NoSQL database, referring as TrackerDB, is guarateed to be tamperproof but the risk of single point failure still exists.

\cite{TrustedMarketplaceWearable} focuses on trading the sensitive data among wearables. Several security issues are well discussed and solved with DLTs in the paper, the system consists multiple components that has its own responsibility, such as data anonymizer eliminates keen information for privacy protection, access controller handles the key management and contract manager manages Ethereum smart contracts. While the trading processes are splited into multiple servers, and the request/response communication model is applied, the scalability problem of the marketplace remains.
% TODO:補一個 MAM 訂閱未來資料的敘述

In \cite{IOTASensorNode}, sensor nodes (SNs) in distributed sensor node system upload data to IOTA network via MAM protocol, and the Back-End server helps SNs to accelerate transaction attachments. The Back-End server also manages keys of data streams, record a tuple of SN, SN metadata, keys and available data stream entry points on MAM, and evaluates data price according to it's quality. Furthermore, as the Back-End server keeps all information of data products, it operates an user friendly interface of the marketplace and tackles all trading procedures. The Back-End server encounters the system scalability problem, single point failure as well as malicious attacks which may damage the profits of all players.

A similar approach to the previous one, the IOTA-based decentralized data marketplace in \cite{DDMSmartCities} puts data streams on the Tangle via MAM protocol as well. Yet the data marketplace does not exist any intermediate server but data providers only, data providers generate and send data streams to MAM channel, and add a specific tag in transactions as an index that the marketplace application can retreive and show the product information on a map where data consumers can select from. Payments are in IOTA token with the transaction contains another type of tag, which both providers and consumers can double-check. Once the participants grows rapidly, this searching specific transactions by tags approach may fail due to the massive amount of transactions returned. Moreover, it is difficult to filter out the interested information.

Two technical architectures for data trading are directly relevant to our work.
\cite{SocialGood} proposed a smart transportation system that incorporate two DLTs, IOTA and Ethereum and a distributed storage IPFS. Though IOTA provides better scalability, it does not provide distributed computation as Ethereum smart contract. Thus, in this approach, IOTA and Ethereum are adopted to build a secure and smart system application, which is the principle we followed in our approach. Meanwhile, IPFS and MAM are viewed as the data storage in the system, where IPFS stores data that are not convenient to store on public chain and referenced to its hash into MAM transactions. Three types of MAM channels are used interactively to minimize the channel ID and key that data producers need to manage. The access control is examined by Authentication Service, the only client/server communication architecture, where the security issues and bottleneck of system emerges from. Also, the details of trading are not illustrated in this paper.

\subsection{Distributed Storage System}
Decentralized storage systems allow users to store files in a distributed network that is maintained by individual nodes around the world instead of a central service provider. Nevertheless, DLTs are often used as the backbone of these systems as data storage and also an incentive layer to encourage people get involved in the network. Filecoin \cite{FileCoin} in Inter-Planetary File system(IPFS)\cite{IPFS} is an incentive layer to incent nodes to provide storage. IPFS is a content-based addressing storage model in a peer-to-peer network, which users can obtain the data with the unique hash value through the network. However, no cryptographic system is applied for user-uploaded files. Sia\cite{Sia} splits the uploaded file into multiple data segments encrypted with the owner's private key, then cipher text is sent to the Sia nodes that rent the storage in Siacoin through smart contracts. Files are duplicated in multiple nodes to prevent data loss.
